---
title: ""
author: "William Pilcher"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_float: true
---

# This code is a wrapper to perform differential abundance tests for a variety of variables.
# All differetial abundances analyses perform binary comparions between a group with or without an event, adjusting for siteXbatch as a covariate.
# All differential abundances use limma with a robust linear model to fit to the logit-transformed proportions, in a mechanism similar to propeller.
# Logit is preferred for its interpretability as opposed to arcsin-transformations.


```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# Setup
```{r init}
library(ggpubr)
library(survival)
library(survminer)
library(ggplot2)
library(dplyr)
library(gridExtra)
source("source/MMRF_load_dependencies_only.R", local = T)
source("source/Helper_Functions/survival_AFR_functions.R")
# source("source/Helper_Functions/COMMON_diff_abundance_functions.R", local = T)

cluster_group <- "subcluster_V03072023"
output_expr <- file.path(output, "R_Plots_Select", "BulkRNA")

dir.create(output_expr, showWarnings = F, recursive = T)

# floral_fill_theme <- list(
#     "groupA (SIG)" = fill_RP,
#     "groupA" = "#a9bad0",
#     "groupB (SIG)" = "#A48AD3",
#     "groupB" = "#baafcf"
# )

floral_color_theme <- list(
    "SIG (+)" = fill_RP,
    "+" = color_RP,
    "SIG (-)" = fill_NP,
    "-" = color_NP
)

floral_fill_theme <- floral_color_theme
```

# Comprehensive Survival Analysis Function
```{r}
# Comprehensive survival analysis function

```

```{r}
analysis_name <- "Plasma_Cells_bulkRNA"
h5ad_file <- file.path(output, "Plasma_Cells", analysis_name, paste0(analysis_name, "_pydeseq2_filtered_pseudobulked.h5ad"))
# custom_sig_gsva <- file.path(nk_cell_output_path, top_dir, analysis_name, paste0(analysis_name, "_custom_pathways_ulm_scores.csv"))


```



```{r}
packages <- "anndataR"
not_installed <- packages[!(packages %in% installed.packages()[ , "Package"])]    # Extract not installed packages
if(length(not_installed)) remotes::install_github("scverse/anndataR@084a1878c733f0cd7a680bef6a8c52bf1b0f0844", upgrade = "never") # version 0.2 for R 4.4.1


library(anndataR) # scverse/anndataR@084a1878c733f0cd7a680bef6a8c52bf1b0f0844 - version 0.2 for R 4.4.1
adata <- read_h5ad(h5ad_file, mode = "r")
```

# TK1
```{r}
sce <- adata$as_SingleCellExperiment()

sce_subset <- sce[, !is.na(colData(sce)$d_dx_amm_age) & !is.na(colData(sce)$d_amm_tx_asct_1st) & !is.na(colData(sce)$d_pt_sex) & !is.na(colData(sce)$ttcpfs)]
test_output <- perform_gene_survival_analysis(sce_subset, gene_name = "ENSG00000167900", covariates = c("d_dx_amm_age","d_amm_tx_asct_1st",  "d_pt_sex"), cutpoint_method = "optimal")
test_output

```

# TK1 Median
```{r}
test_output <- perform_gene_survival_analysis(sce_subset, gene_name = "ENSG00000167900", covariates = c("d_dx_amm_age","d_amm_tx_asct_1st",  "d_pt_sex"), cutpoint_method = "median")
test_output

```